# Supplemental

## 2023-01-12 {-}

```{r video-powers-of-ten, fig.cap="[[@Eames_Office2010-xd]](https://www.youtube.com/watch?v=0fKBhvDjuy0)"}
knitr::include_url("https://www.youtube.com/embed/0fKBhvDjuy0")
```

### Neuroscience is harder than physics because...{-}

- A. The brain has more parts than any other physical entity we know about.
- B. Physicists have largely ignored biology.
- C. Nervous systems are influenced by multiple factors we can't (yet) measure effectively.
- D. Physicists only study "toy" problems.

### Systems have all of the following components EXCEPT: {-}

- A. Boundaries
- B. Components
- C. Interactions among components
- D. Inputs and outputs
- E. Readily predictable behavior

## 2023-01-17 {- #suppl_2023_01_17}

> *"If understanding everything we need to know about the brain is a mile, how far have we walked?"*
> -- J. Lichtman

```{r suppl-lichtman-video, fig.cap="[[@National_Geographic2014-gv]](https://www.youtube.com/watch?v=nvXuq9jRWKE)"}
knitr::include_url("https://www.youtube.com/embed/nvXuq9jRWKE")
```

### Leonardo da Vinci created wax casts of which fluid-filled structure in the forebrain? {-}

a. Pineal gland
b. Cerebral cortex
c. Cerebral ventricles
d. Hippocampus

### Decartes was a philosophical *dualist*. This means he believed that... {-}

a. Philosophers should engage in armed combat over their ideas
b. *Human* behavior is influenced by physical and extra-physical (spiritual) forces
c. The pineal gland is both an input and output structure

### This cell stain fills entire neurons, but only a small fraction of the total number {-}

a. Nissl stain
b. Retrograde tracer
c. Golgi stain

### Structural methods have high/low *temporal* resolution {-}

- Justify your answer
